### 2016-02-08 pdocs/thesis/bullet-plasticity.tex
pdocs charpy-results

\section{Simulation of Charpy impact test using \bullet}
\label{sec:bullet-plasticity}

@@

@@

\subsection{Constraint with zero limits}
In this case btGeneric6DofConstraint is used with high and low limits set to zero. 
Constraint is made breakable by setting breakingImpulseThreshold.
This is common technique to provide breakable objects in games and provides visually accetable results for brittle materials.
Constraint forces are obtained using JointFeedback feature. Plastic moment is 64 Nm for default dimensions.

@@

>>>>

\section{Simulation of Charpy impact test using \bullet}
\label{sec:bullet-charpy}

@@

\subsection{Constraint with zero limits}
In this case btGeneric6DofConstraint is used with high and low limits set to zero. 
Constraint is made breakable by setting breakingImpulseThreshold.
This is common technique to provide breakable objects in games and provides visually accetable results for brittle materials.

@@

@@

\section{Charpy impact test results using \bullet}
\label{sec:bullet-charpy-results}

\subsection{Results for single rigid body}
Timestep of 0.1 ms provides expeced results and specimen bounces hammer back.
Larger timesteps produce various kinds of unexpected results like
\begin{itemize}
\item Specimen goes trough anvil and penetrates hammer
\item Specimen moves sideways and stays on anvil. This can be seen e.g. by setting timestep to 17 ms and leaving hammer draft away.
\end{itemize}

\subsection{Results for constraint with zero limits}
This technique provides effective and stable way to simulate breaking into two objects. 
Required energy to break constraint can be controlled using
breakingImpulseThreshold.

\subsection{Results for springConstraint}
Energy loss is in right scale but visual feedback is not realistic as specimen gets back to initial shape.
Unstable simulation can be seen by setting yield stress to e.g. 800 MPa.

\subsection{Results for spring2Constraint}
Results are quite similar as for springConstraint but automatic parameter tuning helps in avoiding unstable simulations.
